\chapter{Acknowledgement}
% Gửi lời cám ơn đến thầy

% nhà trường tạo điều kiện học tập

% bạn bè, đồng nghiệp, các anh đi trước, đặc biệt là ABC 

% Cuối cùng cảm ơn gia đình là hậu phương vững chắc để chúng em có thể có tài nguyên cũng như chỗ dựa tinh thần trong suốt quá trình làm luận văn 

First and foremost, we would like to express our respect to our esteemed supervisor Associate Professor Tran Minh Triet, who has always been there for us during our work on this thesis. Thanks to his helpful advice, useful suggestion, continuous encouragement and inspirational motivation, that we are able to have enough strength to complete everything in this work, as well as acquire ourselves an immeasurable level of knowledge. We really do appreciate that. 

Secondly, we want to offer our gratitude to the Faculty of Information Technology at the University of Science, VNU-HCM for their dedicated lecturers.  Most of the core knowledge in this report originates from all the mandatory courses that are well-delivered by them.

Thirdly, we are beholden to all our friends and colleagues at SELAB, University of Science who are always willing to help us relentlessly. In fact, it would be unlikely for us to develop the content of this thesis without all the constructive discussion and interesting suggestions from them.

Last but not least, with our deepest gratefulness, we are wholeheartedly thankful for our family members, for their immeasurable unconditional love and also infinite support, both mental and physical. They have always been our source of motivation to survive our long-lasting four-year university period and especially on the completion of this thesis.
